---
title: "Forecasting E-Commerce Sales"
author: "Ayhan Ertuğlu - ETM58D - Spring 2020"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)

```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="html_document")

```

1. [Codes for Naïve Approach](https://github.com/ETM-58D/spring20-ayhanertuglu/blob/master/files/Project/Project_Naive_Approach.R)

    You may find the code for our first approach of the problem, naive approach.
    
2. [Codes for Linear Regression](https://github.com/ETM-58D/spring20-ayhanertuglu/blob/master/files/Project/Proje_Linear_Regression.R)

    For another method, Linear Regression, the code can be examined.
    
3. [Codes for Gradient Boosting](https://github.com/ETM-58D/spring20-ayhanertuglu/blob/master/files/Project/Project_Gradient_Boosting.R)

    Gradient Boosting is also employed and tested for the forecasting.
    
4. [Codes for CV Penalized Regression](https://github.com/ETM-58D/spring20-ayhanertuglu/blob/master/files/Project/Proje_CV_Penalized_Regression.R)

    CV Penalized Regression method is also utilized. 
    
5. [Codes for Penalized Regression](https://github.com/ETM-58D/spring20-ayhanertuglu/blob/master/files/Project/Project_Penalized Regression.R)

    Our best resulted approach's code can be analyzed from above.
    
6. [Codes for Daily Based One-Week and One-Month Sold Counts](https://github.com/ETM-58D/spring20-ayhanertuglu/blob/master/files/Project/Weekly - Monthly Based Prices.R)

    Daily based sold counts for the past one week and one month can be observed from the link above.
    
7. [Codes for Sold Counts vs Time](https://github.com/ETM-58D/spring20-ayhanertuglu/blob/master/files/Project/Sold Count vs Time.R)

    The raw data's sold counts vs time graph code can be reached from the link above.

